Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-17 analysis/paper/paper.Rmd
Clean up methods removing redundant text

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020).
Statistical analysis were carried out using R 4.1.0 (R Core Team, 2021), the rstanarm (v2.13.1; Gabry & Goodrich, 2016) and the report (v0.2.0; Makowski, Patil, & Lüdecke, 2019) packages. The full reproducible code is available in @Sparks2022.

>>>>

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Pro (13-inch, M1, 2020) using R 4.1.0 (R Core Team, 2021).
